\batcave: Bayesian Analysis Tools for Context-Aware Variant Evaluation

### 2019-09-25 NAR_DRAFT.tex
fix problems with figs 1 and 2

Shi et al.\ performed multi-region whole exome sequencing on 6 individual breast tumors to a mean target sequencing depth of $160\mathrm{X}$ and validated all variants identified by three different variant calling pipelines~\cite{Shi2018}.
%We downloaded aligned reads for this tumor, and called variants with MuTect 1.1.7 as described in Materials \& Methods.
We estimated a per-base mutation rate for this tumor of $4\cdot10^{-8}$. \rngcomment{Any comment on this result?}\bkmcomment{Noone, as far as I can tell has done a systematic calculation for TCGA. \cite{Williams2018} is only out in 2018. On the basis of tumor mutation burden studies breast cancer is one of the slowest mutators, but there is no way to go from TMB to mutation rate since it depends on depth/frequency. The one breast cancer studied in Williams 2018 the estimate at just over 1e-7. that is a whole genome whereas ours is an exome, and theirs is deeper. My argument would be that it is not out of line with previous estimates for breast cancer and it is what the data indicates.}
and the area under the precision-recall curve is identical (.972) for MuTect and \batcave (Figure~\ref{NAR-wes_fig}\textbf{F} and Table \ref{table:01}).
For the validated variants, MuTect and \batcave yield almost identical precision-recall curves (Fig.~\ref{NAR-wes_fig}F and Table~\ref{table:01})

>>>>

Shi et al.\ performed multi-region whole exome sequencing on 6 individual breast tumors to a mean target sequencing depth of $160\mathrm{X}$ and validated all variants identified by three different variant calling pipelines~\cite{Shi2018}.
%We downloaded aligned reads for this tumor, and called variants with MuTect 1.1.7 as described in Materials \& Methods.
We estimated an average per-base mutation rate for these tumor regions of $4\cdot10^{-8}$, which is within the range of observed mutation rates for breast cancers \citep{Alexandrov2019}, and in line with the low number of validated somatic mutations present in these tumors.
and the area under the precision-recall curve is identical (.972) for MuTect and \batcave (Figure~\ref{NAR-wes_fig}\textbf{F} and Table \ref{table:01}).
For the validated variants, MuTect and \batcave yield almost identical precision-recall curves (Fig.~\ref{NAR-wes_fig}F and Table~\ref{table:01})
